Corpus

### 2020-05-11 evaluation/R/corpus-analysis.Rmd

```{r}
pkgs <- read_csv(
  ALL_PACKAGES_DETAILS,
  col_types=cols(
    package = col_character(),
    installed = col_logical(),
    loadable = col_logical(),
    package_native_code = col_double(),
    package_r_code = col_double(),
    package_code = col_double(),
    runnable_code = col_double(),
    runnable_files = col_double(),
    runnable_code_examples = col_double(),
    runnable_code_vignettes = col_double(),
    runnable_code_tests = col_double(),
    runnable_files_examples = col_double(),
    runnable_files_vignettes = col_double(),
    runnable_files_tests = col_double(),
    coverage_expr = col_double(),
    coverage_line = col_double(),
    runnable_success = col_double(),
    runnable_error = col_double(),
    runnable_time = col_double(),
    runnable_rate = col_double(),
    funs_private = col_double(),
    funs_public = col_double(),
    funs = col_double(),
    revdeps = col_double(),
    funs_with_assert = col_double(),
    asserts = col_double(),
    uses_roxygen = col_logical()
  )
)
```

@@

>>>>

```{r}
pkgs <- read_csv(
  CRAN_PACKAGES_DETAILS,
  col_types=cols(
    package = col_character(),
    installed = col_logical(),
    loadable = col_logical(),
    version = col_character(),
    title = col_character(),
    size = col_double(),
    package_native_code = col_double(),
    package_r_code = col_double(),
    package_code = col_double(),
    runnable_code = col_double(),
    runnable_files = col_double(),
    runnable_code_examples = col_double(),
    runnable_code_vignettes = col_double(),
    runnable_code_tests = col_double(),
    runnable_files_examples = col_double(),
    runnable_files_vignettes = col_double(),
    runnable_files_tests = col_double(),
    coverage_expr = col_double(),
    coverage_line = col_double(),
    runnable_success = col_double(),
    runnable_error = col_double(),
    runnable_time = col_double(),
    runnable_rate = col_double(),
    funs_private = col_double(),
    funs_public = col_double(),
    funs = col_double(),
    revdeps = col_double(),
    funs_with_assert = col_double(),
    asserts = col_double(),
    uses_roxygen = col_logical()
  )
)
```

@@

### Reverse dependencies

```{r}
pkgs_revdeps_raw <- read_csv(
  CRAN_REVDEPS, 
  col_types=cols(
    package = col_character(),
    revdep = col_character()
  )
)
corpus_revdeps <- pkgs_revdeps_raw %>% semi_join(corpus, by="package")
write_csv(pkgs_revdeps_raw, CORPUS_REVDEPS)
write_lines(unique(corpus_revdeps$revdep), CORPUS_REVDEPS_UNIQUE)
```

### 2020-05-11 evaluation/R/corpus.Rmd
Draft of 2

Next we pull in some package metadata.

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```

@@

```{r}
write_csv(pkgs, ALL_PACKAGES_DETAILS)
write_lines(pkgs$package, ALL_PACKAGES_FILE)
```

>>>>

Next we pull in some package metadata:

```{r}
pkgs_metadata <-
  read_csv(
    PACKAGE_METADATA,
    col_types=cols(
      package = col_character(),
      package_name = col_character(),
      version = col_character(),
      title = col_character(),
      size = col_double()
    )
  ) %>% select(
    package,
    version,
    title,
    size
  )
```

and size:

@@

```{r joining data}
pkgs <-
  pkgs_cran %>%
  left_join(mutate(pkgs_installed, installed=TRUE), by="package") %>% mutate(installed=replace_na(installed, FALSE)) %>%
  left_join(transmute(pkgs_loadable, package, loadable=TRUE), by="package") %>% mutate(loadable=replace_na(loadable, FALSE)) %>%
  left_join(pkgs_metadata, by="package") %>%
  left_join(pkgs_sloc, by="package") %>%
  left_join(pkgs_runnable_code, by="package") %>%
  left_join(pkgs_coverage, by="package") %>%
  left_join(pkgs_runs, by="package") %>%
  left_join(pkgs_functions, by="package") %>%
  left_join(pkgs_revdeps, by="package") %>%
  left_join(pkgs_asserts, by="package") %>%
  left_join(pkgs_roxygen, by="package")
```

@@

```{r}
write_csv(pkgs, CRAN_PACKAGES_DETAILS)
write_lines(pkgs$package, CRAN_PACKAGES_FILE)
write_csv(pkgs_revdeps_raw, CRAN_REVDEPS)
```
